First steps in synthetic algebraic geometry

### 2017-03-17 snippets/qcoh.tex
Necessity of the representation property

\begin{scholium}Let~$E \in \Zar(S)$ be a quasicoherent~$\affl$-module.
Let~$A \in \Zar(S)$ be a quasicoherent~$\affl$-algebra such that~$\Spec(A) \in
\Zar(S)$ is representable by an object of the site used to define~$\Zar(S)$.
Then the canonical morphism
\[ E \otimes_\affl A \longrightarrow [\Spec(A), E] \]
is an isomorphism.
\end{scholium}

@@

% PSh

>>>>

\begin{scholium}\label{scholium}
Let~$E \in \Zar(S)$ be a quasicoherent~$\affl$-module.
Let~$A \in \Zar(S)$ be a quasicoherent~$\affl$-algebra such that~$\Spec(A) \in
\Zar(S)$ is representable by an object of the site used to define~$\Zar(S)$.
% XXX: "locally representable"?
Then the canonical morphism
\[ E \otimes_\affl A \longrightarrow [\Spec(A), E] \]
is an isomorphism.
\end{scholium}

@@

\begin{rem}The condition in Scholium~\ref{scholium} that~$\Spec(A)$ is
representable by an object of the site used to define~$\Zar(S)$ cannot be
dropped. For instance, if we employ the parsimonious sites and consider~$S =
\Spec \ZZ$,~$A = \K_S^\Zar$, and~$E = \affl$, then~$\Spec(A) = \emptyset$.
Therefore the codomain of the canonical morphism is the zero algebra, but the
domain is not.
\end{rem}
